---
output:
  pdf_document:
    keep_tex: yes
  html_document: default
  word_document: default
---

```{r, echo=FALSE, warning=FALSE, message=F, results='asis'}

library(xtable)
#SET OPTIONS
options(xtable.comment = F)
options(xtable.floating = F)
options(xtable.timestamp = "")
options(width = 100)
# PERIODICITY REPORT OPTION
n = 126
p = 0.98


# ## ----------------------------------------------TESTS------------------------------------------------------
# load(file = "hamfData2.RData")
# testDate = '/20160217'
# sub.exceptions = lapply(lapply(subs.o, dailyExceptions, date = end(subs[testDate])), function(x)return(x*100))
# pof.exceptions = dailyExceptions(pofs[testDate])*100
# uft.exceptions = dailyExceptions(ufts[testDate])*100




# ------------------------REGULAR (NOT TESTS)------------------------------------------------------
source('loadUp.R')
reportDate = end(subs.o$LSE)
m = seq(reportDate, length = 2, by = "-1 month")[2]
m = end(as.xts(index(ufts)[which(index(ufts)<=m)])) 

q = seq(reportDate, length = 2, by = "-1 quarter")[2]
q = end(as.xts(index(ufts)[which(index(ufts)<=q)])) 

y = seq(reportDate, length = 2, by = "-1 year")[2]
y = end(as.xts(index(ufts)[which(index(ufts)<=y)]))

dates = c(reportDate, m,q, y)

#GET VAR EXCEPTIONS
sub.exceptions.98 = lapply(lapply(subs.o,FUN = function(y)return(dailyExceptions(y, n = n))), function(x)return(x*100))
pof.exceptions.98 = dailyExceptions(pofs, n = n)*100
uft.exceptions.98 = dailyExceptions(ufts, n = n)*100
mkt.exceptions.98 = dailyExceptions(mkt, n = n)*100

#Component Risks

compRisks = reportComponentRisks(subs.o, subs.weights, n = n)  

#RISK LEVELS

sub.levels.var = lapply(currentLevelsSubs(subs.o, FUN = "VaR", width = n, omissions = c("MiscLSE", "MiscLSD", "MiscED", "MiscMF", "MiscMN")), function(l)return(l*100))

sub.levels.es = lapply(currentLevelsSubs(subs.o, FUN = "ES", width = n, omissions = c("MiscLSE", "MiscLSD", "MiscED", "MiscMF", "MiscMN")), function(l)return(l*100))

uft.levels.weighted.es = currentLevelsFunds2(funds = ufts, FUN = "ES", p = 0.98, width = n, model = "weights", subs.o = subs.o, weights = subs.weights, mode = "change")*100

# uft.levels.weighted.var = currentLevelsFunds(funds = ufts, FUN = "VaR", p = 0.98, width = n, model = "weights", subs.o = subs.o, weights = subs.weights)*100

uft.levels.var = currentLevelsFunds(ufts, FUN = "VaR", width = n)*100
uft.levels.es = currentLevelsFunds(ufts, FUN = "ES", width = n)*100

pof.levels.var = currentLevelsFunds(pofs, FUN = "VaR", width = n)*100
pof.levels.es = currentLevelsFunds(pofs, FUN = "ES", width = n)*100

mkt.levels.var = currentLevelsFunds(mkt, FUN = "VaR", width = n)*100
mkt.levels.es = currentLevelsFunds(mkt, FUN = "ES", width = n)*100

#Avg cor
cor.list = reportCorrelation(subs.o = subs.o, bm = sp$SPTR, dates = dates, width = n)

#ORGANIZE INTO DATAFRAMES
exceptions.98 = organizeExceptions(pof.exceptions.98, uft.exceptions.98, sub.exceptions.98, mkt.exceptions.98)

levels.es = organizeLevels(pof.levels.es, uft.levels.es, sub.levels.es, mkt.levels.es)
levels.var = organizeLevels(pof.levels.var, uft.levels.var, sub.levels.var, mkt.levels.var)


#MAKE xtable objects
exceptions.98.xList = xtableList(exceptions.98, align = 'rccc')
cor.xList = xtableList(cor.list, align = 'lcccc')
compRisks.xList = xtableList(compRisks, align = 'rccc|c')

levels.weighted.es.xtable = xtable(uft.levels.weighted.es, align = 'rcccc')
#levels.weighted.var.xtable = xtable(uft.levels.weighted.var, align = 'rcccc')

levels.es.xlist = xtableList(levels.es, align = 'rcccc')
levels.var.xlist = xtableList(levels.var, align = 'rcccc')

large = function(x){
    paste0('{\\Large{\\bfseries ', x, '}}')
}
italic = function(x){
    paste0('{\\emph{ ', x, '}}')
}
bold = function(x){
   paste0('{\\bfseries ', x, '}')
}
red = function(x){
   paste0('{\\color{red} ', x, '}')
}

#print.xtableList(test.xList)
```

#Daily Risk Report
### `r reportDate`
##98% VaR Exceptions
```{r, echo=FALSE, warning=FALSE, message=F, results='asis'}
print.xtableList(exceptions.98.xList, floating = T
                 #, colnames.format = "multiple"
                 , sanitize.subheadings.function = italic
                 , sanitize.colnames.function = bold
                 #, sanitize.numbers()
                 , sanitize.rownames.function = bold
                 #, booktabs = T
                 #, table.placement = "Ht"
                 )


```




##Risk Levels At Current Allocations (excluding misc accts)
###Change in Risk Levels
###1. Change in Expected Tail Loss (ES)
```{r, echo=FALSE, warning=FALSE, message=F, results='asis'}
print.xtable(levels.weighted.es.xtable, floating = T
                 #, colnames.format = "multiple"
                 , sanitize.subheadings.function = italic
                 , sanitize.colnames.function = bold
                 #, sanitize.numbers()
                 , sanitize.rownames.function = bold
                 #, booktabs = T
                 #, table.placement = "Ht"
                 )
```




```{r, echo=FALSE, warning=FALSE, message=F, results='asis', fig.width=8, fig.height=3}
l= levelsForBarPlot(currentLevelsFunds2(funds = ufts, FUN = "ES", p = 0.98, width = n, model = "weights", subs.o = subs.o, weights = subs.weights, mode = "levels")*100)

library(ggplot2)
p = ggplot(l, aes(x=Date, y=ExpectedTailLoss, fill = Date))
p = p + geom_bar(position = "dodge", colour = "black", stat = "identity", width = 0.75)
p = p + facet_grid(. ~ fund)
p = p + scale_fill_brewer(palette = 6)
p = p + theme_bw()
p = p + theme(axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), axis.title.y = element_blank(), legend.position = "bottom")
p = p + guides(fill = guide_legend(title = NULL))

#p = p + theme(axis.text.x = element_text(angle = 35, hjust = 1, vjust = 1))
#p = p + facet_grid(fund ~ .)
p

```

\pagebreak

###2. Percent Contribution to Risk
```{r, echo=FALSE, warning=FALSE, message=F, results='asis'}
print.xtableList(compRisks.xList, floating = T
                 #, colnames.format = "multiple"
                 , sanitize.subheadings.function = italic
                 , sanitize.colnames.function = bold
                 #, sanitize.numbers()
                 , sanitize.rownames.function = bold
                 #, booktabs = T
                 #, table.placement = "Ht"
                 )
```

\pagebreak

##Average Correlations
> *Average correlation of current subadvisors to the S&P 500 over previous 26 weeks*
> *Average correlation between subadvisors over previous 26 weeks*

```{r, echo=FALSE, warning=FALSE, message=F, results='asis'}
print.xtableList(cor.xList, floating = T
                 #, colnames.format = "multiple"
                 , sanitize.subheadings.function = italic
                 , sanitize.colnames.function = bold
                 #, sanitize.numbers()
                 , sanitize.rownames.function = bold
                 #, booktabs = T
                 #, table.placement = "Ht"
                 )

lse.cor.sp = rollAvgCorToBM(subs.o$LSE, sp$SPTR, width = n)
lsd.cor.sp = rollAvgCorToBM(subs.o$LSD, sp$SPTR, width = n)
mn.cor.sp = rollAvgCorToBM(subs.o$MN, sp$SPTR, width = n)
mf.cor.sp = rollAvgCorToBM(subs.o$MF, sp$SPTR, width = n)
avg.cor.sp = cbind(lse.cor.sp, lsd.cor.sp, mf.cor.sp, mn.cor.sp)
names(avg.cor.sp)[1:4] = paste0(c("LSE", "LSD", "MF", "MN"), rep("AvgCor", 4))

avgCor.list = lapply(subs.o, FUN = function(x)return(extractAvgCorrelation(rollingCorrelationMatrix(x, window = n))))
avgCor = avgCor.list[[1]]
for (i in 2:length(avgCor.list))
{
    avgCor = cbind(avgCor, avgCor.list[[i]])
}
colnames(avgCor) = names(avgCor.list)

require(ggplot2)
require(data.table)
data = avg.cor.sp
dt = data.table(data.frame(Date = as.Date(index(data)), LSE = data[,1], LSD = data[,2], MF = data[,3], MN = data[,4], row.names = NULL))
dt.m = melt(dt, 'Date')
names(dt.m)[2:3] = c("Legend", "AverageCorrelation")
p = ggplot(dt.m,aes(x=Date,y=AverageCorrelation,group=Legend,color=Legend)) + geom_line() + scale_x_date()
#p = p + theme_minimal()
p = p + theme_bw()
p = p + ggtitle("Avg Correlation to S&P 500")
p

data = avgCor
dt = data.table(data.frame(Date = as.Date(index(data)), ED = data[,1], LSE = data[,2], LSD = data[,3], MF = data[,4], MN = data[,5], row.names = NULL))
dt.m = melt(dt, 'Date')
names(dt.m)[2:3] = c("Legend", "AverageCorrelation")
p = ggplot(dt.m,aes(x=Date,y=AverageCorrelation,group=Legend,color=Legend)) + geom_line() + scale_x_date()
#p = p + theme_minimal()
p = p + theme_bw()
p = p + ggtitle("Avg Correlation Between SubAdvisors in Strategy")
p

```

##Daily Modified VaR Levels
### `r reportDate`
```{r, echo=FALSE, warning=FALSE, message=F, results='asis'}
print.xtableList(levels.var.xlist, floating = T
                 #, colnames.format = "multiple"
                 , sanitize.subheadings.function = italic
                 , sanitize.colnames.function = bold
                 #, sanitize.numbers()
                 , sanitize.rownames.function = bold
                 #, booktabs = T
                 #, table.placement = "Ht"
                 )
```
\pagebreak

##Daily 98% Expected Shortfall (Modified Conditional VaR) Levels
### `r reportDate`



> *Expected shortfall is the average expected loss beyond the VaR level, i.e. how much you expect to actually lose when the VaR level is breached.*



```{r, echo=FALSE, warning=FALSE, message=F, results='asis'}
print.xtableList(levels.es.xlist, floating = T
                 #, colnames.format = "multiple"
                 , sanitize.subheadings.function = italic
                 , sanitize.colnames.function = bold
                 #, sanitize.numbers()
                 , sanitize.rownames.function = bold
                 #, booktabs = T
                 #, table.placement = "Ht"
                 )
```



